---
title: "Lindstrom - Diagnosis count clean"
output:
  html_document:
    theme: flatly
    toc: true
    toc_depth: 3
    toc_float: true
    df_print: paged
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
---

```{r setup, echo=T, results='hide', message=F, warning=F}
library(tidyverse)
library(janitor)
library(readxl)
```

## Goal of notebook

To inspect the data and do any cleanup or renaming. Further analysis will be in other notebooks.

## Import

```{r read}
data <- read_excel("data-raw/Children with Diagnosis 2106 to 2020.xlsx") %>% clean_names() %>% arrange(id, cal_yr)

# peek at the data
data %>% glimpse()
```

## Data smells

If `id` is a unique child then we have multiples. Kids can be abandoned more than once, so maybe not a big deal.

```{r smell_id}
data %>% 
  count(id) %>% 
  arrange(n %>% desc()) %>% 
  filter(n > 1)
```

```{r smell_id_detail}
data %>% 
  filter(id == "DD3XV285")
```

### Checking duplicates

This one is suspect because it is exactly the same. Details make two real records unlikely.

```{r smell_dupes}
data %>% 
  get_dupes()
```
### Peek at removal_reason

```{r peek_reason}
data %>% 
  count(removal_reason)
```

### Peek at latest placement

```{r peek_placement}
data %>% 
  count(latest_placement)
```

### Peek permanency_plan

```{r peek_plan}
data %>% 
  count(permanency_plan)
```

### Peek at race_ethnicity

```{r peek_race}
data %>% 
  count(race_ethnicity)
```

## Rename some columns

```{r rename_cols}
diagnosis_clean <- data %>% 
  rename(
    separation_disorders = attachment_disorder_separation_anxiety_disorder,
    congnitive = developmentally_disabled_cognitive_disorder,
    fetal_alcohol_drug = fetal_alcohol_syndrome_infant_drug_exposure,
    mobility_impaired = mobility_impaired_physically_disabled
  )
```

## Export data

```{r export}
diagnosis_clean %>% 
  write_rds("data-processed/diagnosis_clean.rds")
```

