---
title: "Lindstrom - Diagnosis count clean"
output:
  html_document:
    theme: flatly
    toc: true
    toc_depth: 3
    toc_float: true
    df_print: paged
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
---

```{r setup, echo=T, results='hide', message=F, warning=F}
library(tidyverse)
library(janitor)
library(readxl)
```

## Goal and purpose

- You want the count and percentage of kids that have at least one diagnosis. (But isn’t that all of them here?)
- You want the count and percentage of kids with more than one diagnosis (i.e, more than one column with a result). Better yet, the count of the different diagnosis for each kid.
- You want to categorize the diagnosis into three buckets: medical, mental/behavioral and developmental. Then you want to know how many kids have a diagnosis in more than one bucket.

## Ideas

- I could do 1 or 0 as true for each disorder type.
- I'd like to name the disorder type with the classification: mb_ptsd, m_asthma, d_learning_disability
- by using a number, I can then sum across rows to get totals.
- by having the categorization, I could do that using `starts_with("mb_")`, etc.

## Import

```{r}
data <- read_excel("data-raw/Children with Diagnosis 2106 to 2020.xlsx") %>% clean_names() %>% arrange(id, cal_yr)
# peek
data %>% glimpse()
```

## Data smells

If `id` is a unique child then we have multiples. Kids can be abandoned more than once, so maybe not a big deal.

```{r}
data %>% 
  count(id) %>% 
  arrange(n %>% desc()) %>% 
  filter(n > 1)
```

```{r}
data %>% 
  filter(id == "DD3XV285")
```

### Checking duplicates

```{r}
data %>% 
  get_dupes()
```

### Peeking at latest placement

```{r}
data %>% 
  count(latest_placement)
```

### Peeking permanency_plan

```{r}
data %>% 
  count(permanency_plan)
```

## Peek race_ethnicity

```{r}
data %>% 
  count(race_ethnicity)
```

## Rename some columns

```{r}
diagnosis_clean <- data %>% 
  rename(
    separation_disorders = attachment_disorder_separation_anxiety_disorder,
    congnitive = developmentally_disabled_cognitive_disorder,
    fetal_alcohol_drug = fetal_alcohol_syndrome_infant_drug_exposure,
    mobility_impaired = mobility_impaired_physically_disabled
  )
```

## Export data

```{r}
diagnosis_clean %>% 
  write_rds("data-processed/diagnosis_clean.rds")
```

