---
title: "Lindstrom - Diagnosis counts"
output:
  html_document:
    theme: flatly
    toc: true
    toc_depth: 3
    toc_float: true
    df_print: paged
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
---

## Setup

```{r setup, echo=T, results='hide', message=F, warning=F}
library(tidyverse)
library(janitor)
library(readxl)
library(DT)
```


## Goal and purpose

- You want the count and percentage of kids that have at least one diagnosis. (But isn’t that all of them here?)
- You want the count and percentage of kids with more than one diagnosis (i.e, more than one column with a result). Better yet, the count of the different diagnosis for each kid.
- You want to categorize the diagnosis into three buckets: medical, mental/behavioral and developmental. Then you want to know how many kids have a diagnosis in more than one bucket.

## Questions

- If `id` is a unique child, then some of these are the same kids abandoned more than once.
- there is also one pure duplicate. See diagnosis-01-import.

## Import

Brings in cleaned data from diagnosis-01-import.

```{r read}
abandon <- read_rds("data-processed/diagnosis_clean.rds")
abandon %>% glimpse()
```

## Create truthy diagnosis

The idea here is to create new columns (with structured names) that has "1" if the diagnosis is present in that column. Since any text equates to a diagnosis per Lindstrom editing, I do this by setting to "1" if not NA.

I can structure the column name as a category by starting the name with a category, like "a_ptsd" or "b_asthma".

> We can update this later with real categories.

```{r create_diag}
abandon_cats <- abandon %>% 
  mutate(
    # I need to do some checking on this to make sure I have each column
    a_add_adhd = case_when(is.na(add_adhd) ~ 0, TRUE  ~  1),
    a_odd = case_when(is.na(odd) ~ 0, TRUE  ~  1),
    b_adjustment_disorder = case_when(is.na(adjustment_disorder) ~ 0, TRUE  ~  1),
    b_anxiety_disorder = case_when(is.na(anxiety_disorder) ~ 0, TRUE  ~  1),
    b_other = case_when(is.na(other) ~ 0, TRUE  ~  1),
    c_asthma = case_when(is.na(asthma) ~ 0, TRUE  ~  1),
    c_allergies = case_when(is.na(allergies) ~ 0, TRUE  ~  1),
    a_separation_disorders = case_when(is.na(separation_disorders) ~ 0, TRUE  ~  1),
    a_autism = case_when(is.na(autism) ~ 0, TRUE  ~  1),
    a_bipolar = case_when(is.na(bipolar) ~ 0, TRUE  ~  1),
    a_conduct_disorder = case_when(is.na(conduct_disorder) ~ 0, TRUE  ~  1),
    a_anemia = case_when(is.na(anemia) ~ 0, TRUE  ~  1),
    a_depression = case_when(is.na(depression) ~ 0, TRUE  ~  1),
    a_disruptive_behavior_disorder = case_when(is.na(disruptive_behavior_disorder) ~ 0, TRUE  ~  1),
    a_cerebral_palsey = case_when(is.na(cerebral_palsey) ~ 0, TRUE  ~  1),
    a_congnitive = case_when(is.na(congnitive) ~ 0, TRUE  ~  1),
    a_diabetes = case_when(is.na(diabetes) ~ 0, TRUE  ~  1),
    a_dysthymic_disorder = case_when(is.na(dysthymic_disorder) ~ 0, TRUE  ~  1),
    a_disassociative_disorders = case_when(is.na(disassociative_disorders) ~ 0, TRUE  ~  1),
    a_failure_to_thrive = case_when(is.na(failure_to_thrive) ~ 0, TRUE  ~  1),
    a_downs_syndrome = case_when(is.na(downs_syndrome) ~ 0, TRUE  ~  1),
    a_enuresis_encopresis = case_when(is.na(enuresis_encopresis) ~ 0, TRUE  ~  1),
    a_emotionally_disturbed = case_when(is.na(emotionally_disturbed) ~ 0, TRUE  ~  1),
    a_hearing_impaired = case_when(is.na(hearing_impaired) ~ 0, TRUE  ~  1),
    a_fetal_alcohol_drug = case_when(is.na(fetal_alcohol_drug) ~ 0, TRUE  ~  1),
    a_mental_retardation = case_when(is.na(mental_retardation) ~ 0, TRUE  ~  1),
    a_pervasive_developmental_disorder = case_when(is.na(pervasive_developmental_disorder) ~ 0, TRUE  ~  1),
    a_schizoaffective_schizophrenia = case_when(is.na(schizoaffective_schizophrenia) ~ 0, TRUE  ~  1),
    a_impulse_control_disorder = case_when(is.na(impulse_control_disorder) ~ 0, TRUE  ~  1),
    a_intellectual_disability = case_when(is.na(intellectual_disability) ~ 0, TRUE  ~  1),
    a_visually_impaired = case_when(is.na(visually_impaired) ~ 0, TRUE  ~  1),
    a_learning_disability = case_when(is.na(learning_disability) ~ 0, TRUE  ~  1),
    a_mobility_impaired = case_when(is.na(mobility_impaired) ~ 0, TRUE  ~  1),
    a_ptsd = case_when(is.na(ptsd) ~ 0, TRUE  ~  1),
    a_sex_disorder_paraphilia = case_when(is.na(sex_disorder_paraphilia) ~ 0, TRUE  ~  1),
    a_neurological_disorders = case_when(is.na(neurological_disorders) ~ 0, TRUE  ~  1),
    a_expectant_youth = case_when(is.na(expectant_youth) ~ 0, TRUE  ~  1),
    a_respiratory_failure = case_when(is.na(respiratory_failure) ~ 0, TRUE  ~  1),
    a_mood_disorder = case_when(is.na(mood_disorder) ~ 0, TRUE  ~  1),
    a_speech_disability = case_when(is.na(speech_disability) ~ 0, TRUE  ~  1),
    a_personality_disorder = case_when(is.na(personality_disorder) ~ 0, TRUE  ~  1),
    a_other_with_diagnosis = case_when(is.na(other_with_diagnosis) ~ 0, TRUE  ~  1),
    # more as needed
  )
```

## Diagnosis totals

Creates `diag_count` columns that sum diagnosis each category and then the total.

```{r create_totals}
abandon_cats_totaled <- abandon_cats %>% 
  rowwise() %>% 
  mutate(
    diag_count_a = sum(c_across(starts_with("a_"))),
    diag_count_b = sum(c_across(starts_with("b_"))),
    diag_count_c = sum(c_across(starts_with("c_"))),
    diag_count_total = sum(c_across(starts_with(c("a_","b_", "c_")))), # include all cat_ columns
  )
```


### Rows with 2+ diagnosis

Filters for `diag_count_total` with more than 1 then counts the rows.

```{r count_diag_gt_two}
abandon_cats_totaled %>% 
  filter(diag_count_total > 1) %>% 
  nrow()
```

### Testing diagnosis counts

This shows proof of concept that the diag_counts work. The diag_count_total was independently calculated from all cat_ columns.

```{r cats_totaled}
abandon_cats_totaled %>% 
  select(id, starts_with("diag_count_")) %>% 
  datatable()
```

