---
title: "DFCS look"
output:
  html_document:
    theme: flatly
    toc: true
    toc_depth: 3
    toc_float: true
    df_print: paged
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
---

```{r setup, echo=T, results='hide', message=F, warning=F}
library(tidyverse)
library(janitor)
library(readxl)
library(tidytext)
```

## Import

```{r}
data <- read_excel("data-processed/Lindstrom-DFCS-Data.xlsx") %>% clean_names()
```

## Cleaning

Taking a look:

```{r}
data %>% glimpse()
```


## New idea

I could go through the original diagnosis column and look for the same keywords.

Developmentally Disabled##Infant Drug Addiction/Prenatal Drug Exposed

## Cleaning diagnosis

We need to set up search variable for the categories and the columns.

### Capture the columns

```{r}
cols_diag <- data %>% 
  select(contains("diagnoses_")) %>%
  names() %>% 
  tibble::enframe(name = NULL) %>% 
  rename(diag = value)

cols_diag
```

### Categories list

Alcohol-related

```{r}
list_alcohol <- c("alcohol")
```


```{r}
data %>% 
  count(diagnoses)
```


## Diagnosis issues

The field includes multiple values separated by `##`. Teasing out this data might require making a new data set.


## Various explore

```{r}
data %>% 
  filter(str_detect(diagnoses,"Anxiety")) %>% 
  select(diagnoses)
```

